---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# log4r-demo

<!-- badges: start -->
<!-- badges: end -->

The goal of log4r-demo is to showcase how log4r can work under various scenarios.

In the upcoming release, log4r will use namespaced functions, so lets start using that now:

```{r}
library(log4r)
log_info <- log4r::info
log_warn <- log4r::warn
log_error <- log4r::error
log_debug <- log4r::debug
```

```{r}
start_time <- Sys.time() - 1.5 # lets pretend to let this work for 1.5 seconds
logger <- logger(threshold = "DEBUG", appenders = console_appender(logfmt_log_layout()))
log_debug(
  logger, 
  message = "processed entries", 
  file = whereami::whereami(), # if we want to know where this is coming from
  duration = difftime(Sys.time(), start_time, units = "secs")
)
```

One of the other nice things is functions invoked as fields will only
be evaluated if they are used.

For example:

```{r}
did_i_run <- function(context) {
  message("yes I ran in context: ", context)
  return(context)
}
logger <- logger(appenders = console_appender(logfmt_log_layout()))
did_i_run("in chunk")

# this will print and also store the context in the output
log_info(logger, message = "an info message", output = did_i_run("in info log"))

# if this were to eagerly evaluate this would print "yes I ran in context: in debug log" even if the log doesn't print
log_debug(logger, message = "a debug message", output = did_i_run("in debug log"))

# prove code evaluated all the way through here
did_i_run("after log messages")
```

This means you can invoke pontentially "expensive" computation in
debug messages without worrying about them being unnecessarily executed.

<details>
```{r}
sessionInfo()
```
</details>

